\documentstyle[12pt,art12cox,epsf]{article}

\newcommand{\afni}{{\it AFNI\,}}
\newcommand{\afnit}{{\it AFNI\/}\ }
\newcommand{\tothreed}{{\sf to3d\,}}
\newcommand{\tothreedit}{{\sf to3d\/}\ }
\newcommand{\MCW}{{\sf MCW}}

\setlength{\topmargin}{0.0in}
\setlength{\textheight}{9.02in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}

\hyphenpenalty=200

\def\mypleft{\footnotesize \MCW$\!$ \afnit 2.00}
\def\mypright{\scriptsize\today}
\dashpage

\raggedbottom

\newcommand{\seeme}[1]%
{\marginpar{\raggedright%
$\star\star\star$\hspace*{0pt plus 1fill}$\longrightarrow$\\{}%
\scriptsize\bf#1}}

\newcommand{\blob}{\hspace*{1em}}

\setlength{\fboxsep}{1.3pt}
\setlength{\fboxrule}{0.6pt}
\newcommand{\button}[1]{\fbox{\tt #1}}

\newcommand{\mysec}[1]{%
\vspace{1.1in}\goodbreak\vspace{-1.09in}\section{#1}}

\newcommand{\mysubsec}[1]{%
\vspace{0.9in}\goodbreak\vspace{-0.89in}\subsection{#1}}

\newcommand{\mysubsubsec}[1]{%
\vspace{0.8in}\goodbreak\vspace{-0.8in}\subsubsection{#1}}

%---------------------------------------------------------------------
\begin{document}
\thispagestyle{empty}
\small
\vspace*{0pt plus 1fill}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5ex}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.6in}

\displayline{Disclaimer:}
\MCW$\!$~\afni, its associated programs, and its documentation are provided
as is, and no warranty for their correctness or usefulness for any
purpose is made or implied by the Medical College of Wisconsin (\MCW),
or by the author of the software.  Neither \MCW\ nor the author
accepts any liability for any
defects in this software or its manuals, or for any damages caused by use of this
software.

\displayline{Ownership, Conditions of Use, and Restrictions:}
\begin{itemize}\vspace*{-4.9ex}\setlength{\parindent}{0em}\setlength{\parskip}{0.1ex}
   \item Permission is granted to make use of and to make copies of the
        \MCW$\!$~\afnit software and documentation for research
        purposes only.  Ownership of \MCW$\!$~\afnit and all copies is retained by the
        Medical College of Wisconsin.

   \item Patient-care applications are not recommended.  \MCW$\!$~\afnit has not
        been evaluated by or approved by the United States Food and Drug Administration,
        or by any other agency.

   \item Use by for-profit organizations is restricted to one computer system
         per registration.  The derivation of commercial products, directly
         or indirectly, from \MCW$\!$~\afnit is prohibited.
%%%         Use for {\it any\/} purpose
%%%         by for-profit organizations is prohibited without prior arrangement
%%%         and written permission.

   \item Redistribution of \MCW$\!$~\afni, or any derived work, outside the receiving
        institution is prohibited without prior permission.

   \item Copies may be made within non-commercial institutions without separate
        permission from the Medical College of Wisconsin.

   \item Technical support ({\it e.g.},~the fixing of bugs, the explanation
         of documentation, etc.)\ for\ \MCW$\!$~\afnit is not guaranteed.
\end{itemize}
I agree to abide by the terms and restrictions above.\vspace{2ex}

{\bf SIGNATURE}:\vspace{2ex}


{\bf NAME}:\\
(print clearly, or type)\vspace{2ex}

{\bf DATE}:\vspace{2ex}

{\bf E-MAIL ADDRESS}:\\
(print \underline{\bf very} clearly, or type)\vspace{0.5ex}

\displayline{To Register}
Copy this page onto your departmental or institutional letterhead
(or otherwise indicate clearly your affiliation),
sign and date, include your e-mail address, and return via mail or FAX to\\[.5ex]
\hspace*{3em} Robert W. Cox, PhD \\
\hspace*{3em} Biophysics Research Institute \\
\hspace*{3em} Medical College of Wisconsin \\
\hspace*{3em} 8701 Watertown Plank Road \\
\hspace*{3em} Milwaukee WI 53226 USA\\[0.5ex]
\hspace*{3em} FAX: 414--456--6512 \\[0.5ex]
Instructions on how to obtain \MCW$\!$~\afnit by {\tt anonymous ftp} and/or via the WWW
will be sent by e-mail.

\end{document}
